---
title: "Introduction to rdnnmcshap"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to rdnnmcshap}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Overview

The `rdnnmcshap` package provides an R interface to the Python
`dnnmcshap` package via `reticulate`. It implements a three-stage
framework for health insurance cost analysis:

1. **DNN Prediction** -- A bias-free funnel Deep Neural Network
2. **Monte Carlo Simulation** -- Parametric profile generation
3. **Shapley Attribution** -- SHAP-based feature importance with
   conditional analysis

## Installation

First install the Python package:

```{r, eval=FALSE}
reticulate::py_install("dnnmcshap", pip = TRUE)
```
Then install the R package:

```{r, eval=FALSE}
# From source
install.packages("rdnnmcshap", repos = NULL, type = "source")
```

## Quick start

```{r}
library(rdnnmcshap)

# Load a trained checkpoint
ckpt <- load_checkpoint("path/to/model.pth")
model <- ckpt$model
standardiser <- ckpt$standardiser

# Generate MC profiles
marginals <- estimate_marginals(df_raw)
df_mc <- generate_mc_profiles(10000L, marginals)

# Encode and score
X_mc <- encode_profiles(df_mc)
y_mc <- score_dnn(model, X_mc, standardiser)
```
